---
title: "Blog Stats"
author: "Fiverr"
date: "April 1, 2016"
output: html_document
---
# Initial look into the data
```{r echo=FALSE , message=FALSE}

library(xlsx)
library(dplyr)
library(ggplot2)
library(GGally)
file <- "C:/Users/Shobeir/Desktop/Fiverr/20160401/Book1.xlsx"
mydata <- read.xlsx(file,sheetIndex = 1,colClasses = c("character"))
mydata <- tbl_df(mydata)
```

Let's initially, look at the data.
```{r, echo=FALSE}
head(mydata)
```
In order to get a more meanigful look into the data I will add two more columns: 

1.  `posneg` shows if the **ROI** is higher than the average **ROI**.
2.  `dweekday` which shows if the data is from weekend or weekday.
        

```{r echo = FALSE, warning=FALSE}
mydata = mutate(mydata,posneg = as.factor(ifelse(mydata$ROI > mean(mydata$ROI),"plus","minus")),dweekday = as.factor (ifelse(grepl(pattern = "^S",mydata$Date),"WEnd","WDay")))

gmydata <- group_by(mydata,posneg,dweekday)

a <- summarise(gmydata, meanCost = mean(Cost), meanBounce = mean(Bounce),meanPageSess = mean(Pages...Sesssion),
               meanSessDuration = mean(Sess.Duration), meanX = mean(X.cover), meanROI = mean(ROI))

```
Based on the mentioned parameters, I construct a new table based on the average values of the parameters by grouping them into weekday/weekend and Above/Below average ROI.

```{r echo=FALSE}
a <- tbl_df(a)
a
```


Let's dig deeper into the data:


```{r echo=FALSE,message=FALSE}
ggpairs(a)

```

# Conclusion:

In conclusion, the main two factors seem to be the `X.Cover` and `Bounce`. There is a very high correlation between `ROI` and `X.Cover`.